Title

### 2012-07-10 inc/external_forces/external_forces.tex
(hopefully) clarified some of the notation and explaination of the purely mathematical parts of the extension

\subsection{Mathematical Formulation of External Force Contribution}
\ref{eq:potential_integral} is the entry point for the internal Coulombic repulsion force; since both potentials and integrals are linear, one may add additional potentials so that it becomes
\begin{equation}
  \begin{split}
    \Phi(\vec{r};t) \rightarrow & \int d\vecprime{r} \left( V(\vec{r} - \vecprime{r}) + \sum V_{ext}(\vec{r}) \right) n(\vecprime{r}; t) \\
    = & \int d\vecprime{r} V(\vec{r} - \vecprime{r}) n(\vecprime{r}; t) + \sum \int d\vecprime{r} V_{ext}(\vec{r}) n(\vecprime{r}; t) \\
    = & \Phi(\vec{r};t) + \Phi_{ext}(\vec{r};t)
  \end{split}
\end{equation}
This form of $\Phi(\vec{r};t)$ can be substituted into the definition of $K^{force}$ (\ref{eq:Kforce}), again in the basis defined in \ref{eq:coordinate_vector} 
\begin{equation}
  \begin{split}
    K^{force}_{ij} \rightarrow & \frac{1}{N} \int u_i u_j \frac{\partial f}{\partial \vec{p}} \frac{\partial}{\partial \vec{r}} \left( \Phi(\vec{r};t) + \Phi_{ext}(\vec{r};t) \right) d\vec{r} d\vec{p} \\
    \equiv & K^{int}_{ij} + \sum K^{ext}_{ij}
  \end{split}
\end{equation}
where $K^{int}$ is simply the old $K^{force}$. Noting that the spatial derivative of a potential is just the force, we can now define the matrix contributed by each external force is given by
\begin{equation} \label{eq:Kint}
  K^{ext}_{ij} = \frac{1}{N} \iint u_i u_j \left [ \frac{\partial}{\partial \vec{p}} f(\vec{r}, \vec{p}; t) \right ] \cdot \vec{F}_{ext}\;d^{3}x\,d^{3}p
\end{equation}
Finally, the general form of \ref{eq:gaussian_integral_dt_k} for (possibly multiple) external force ($\vec{F}_{ext}$) contributions is now
\begin{equation}
  \frac{\partial}{\partial t} A^{-1}_{ij} = K^{flow}_{ij} + K^{int}_{ij} + \sum K^{ext}_{ij}
\end{equation}

>>>>

Besides a set of initial conditions, the Analytic Gaussian model presented by Michalik and Sipe (see Section \ref{sec:ms_model}) is only useful for modeling free-space propagation.
This is because there is no allowance for external forces, such as those imparted by the ``optical'' elements of an electron microscope column.

\subsection{Mathematical Formulation of External Force Contribution}

While the free-space AG model does not contain any external forces, it does include an internal force.
The Coulomb force is included to model the repulsion of the pulse's electrons from each other.
Because this force is self-influencing, it is the major souce of complexity in the model; indeed without this term, a complete analytic solutions is possible, which is identically ``Gaussian'' optics.\cite{michalik_analytic_2006}

The internal Coulombic repulsion force enters the model in \ref{eq:potential_integral}.
Since both potentials and integrals are linear, one may add additional potentials so that it becomes
\begin{equation}
  V(\vec{r} - \vecprime{r}) \rightarrow V(\vec{r} - \vecprime{r}) + \sum_{k} V_{k}^{ext}(\vec{r})
\end{equation}
Following this new term through the derivation, we see that
\begin{equation}
  \begin{split}
    \Phi(\vec{r};t) = & \int d\vecprime{r} \left( V(\vec{r} - \vecprime{r}) + \sum_{k} V_{k}^{ext}(\vec{r}) \right) n(\vecprime{r}; t) \\
    = & \int d\vecprime{r} V(\vec{r} - \vecprime{r}) n(\vecprime{r}; t) + \sum_{k} \int d\vecprime{r} V_{k}^{ext}(\vec{r}) n(\vecprime{r}; t) \\
    \equiv & \Phi^{int}(\vec{r};t) + \sum_{k} \Phi_{k}^{ext}(\vec{r};t)
  \end{split}
\end{equation}
Therefore each external force contributes an additional term defined as
\begin{equation}
  \Phi^{ext}(\vec{r};t) \equiv \int d\vecprime{r} V^{ext}(\vec{r}) n(\vecprime{r}; t)
\end{equation}
These external terms are not self-influencing, and thus are not subject to the complexities of the internal Coulombic repulsion force. For clarity we now define $\Phi^{int}(\vec{r};t)$ as the old $\Phi(\vec{r};t)$, which results from the Coulomb force, while our new $K^{force}$ now includes these exteral terms.

This form of $\Phi(\vec{r};t)$ can now be substituted into the definition of $K^{force}$ matrix (\ref{eq:Kforce}), again in the basis defined in \ref{eq:coordinate_vector} 
\begin{equation}
  \begin{split}
    K^{force}_{ij} = & \frac{1}{N} \int u_i u_j \frac{\partial f}{\partial \vec{p}} \frac{\partial}{\partial \vec{r}} \left( \Phi(\vec{r};t) + \sum_{k} \Phi_{k}^{ext}(\vec{r};t) \right) d\vec{r} d\vec{p} \\
    \equiv & K^{int}_{ij} + \sum_{k} (K_{k}^{ext})_{ij}
  \end{split}
\end{equation}
Like the potential integrals, we are left with an additional matrix for each external force. Again, for clarity, we now define $K^{int}$ as the $K$ matrix resulting from the internal Coulombic repulsion.

Noting that the spatial derivative of a potential is just the force, we can now define the matrix contributed by each external force is given by
\begin{equation} \label{eq:Kint}
  K^{ext}_{ij} = \frac{1}{N} \iint u_i u_j \left [ \frac{\partial}{\partial \vec{p}} f(\vec{r}, \vec{p}; t) \right ] \cdot \vec{F}_{ext}\;d^{3}x\,d^{3}p
\end{equation}
Finally, the general form of \ref{eq:gaussian_integral_dt_k} for (possibly multiple) external force ($\vec{F}_{ext}$) contributions is now
\begin{equation}
  \frac{\partial}{\partial t} A^{-1}_{ij} = K^{flow}_{ij} + K^{int}_{ij} + \sum K^{ext}_{ij}
\end{equation}
